Tutorial: Quantifying Spatially Resolved Hydration Thermodynamics Using Grid Inhomogeneous Solvation Theory [Article v\versionnumber]

### 2024-06-04 manuscript/manuscript.tex
Update manuscript.tex

The most accurate method to compute a reference energy is to run a GIST calculation of the pure solvent using the same energy method (PME/GPU) and a similar box size, and then compute the average solvent-solvent energy per molecule.

>>>>

The most accurate method to compute a reference energy is to run a GIST calculation of the pure solvent using the same energy method (PME/GPU), a similar box size, at the same temperature and pressure and then compute the average solvent-solvent energy per molecule.
